Improving the Replicability of Psychological Science Through Pedagogy

### 2017-05-19 paper/paper.Rmd
minor revs for mcf action items

These statistical findings mask a more optimistic message, however: In most of our projects, the next step for a motivated experimenter is clear. For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials. In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample. And in some, differences of population would mean that followups would require further stimulus or task adaptation. More generally, we believe that our work here underscores the importance of iterated replication [@lewis2016].

@@

Our experiences performing and compiling the studies here sheds light on one further concern that we believe has been under-reported in past studies [including @osc2015]. Our standard model of replication is based on the notion of a single statistical test -- and its associated effect size -- being the key properties of a study that can be targeted for replication. Yet, as we mentioned above, selecting this key statistical test was difficult for most of the projects in our sample, and virtually impossible for some. We were often forced to consult other sections of the papers (e.g., abstracts, discussion sections) to gain clarity on what test was considered the critical one for the authors' interpretation. It is likely that some of our decisions would not be ratified by the original authors.

@@

In our view, two recommendations will improve this situation dramatically. First, pre-registration typically requires the selection of particular statistical analyses to be designated as critical for interpretation. Were this information available, it would have simplified the problem of selecting effects to replicate in several cases. Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here. In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is thus an important route for more flexible reuse.

>>>>

One potential concern about our project is that our replications might be of lower quality, due to the lead role played by inexperienced investigators. This issue should be taken seriously by any instructor interested in doing replications in the classroom, but we believe it is not a major concern in the current case. First, our experimenters were graduate students, conducting other research in addition to their work in our class. Many of them will go on to publish in top journals (often alongside more senior collaborators), and this work will be treated on its merits, not on the basis of the experience level of the lead author. Indeed, evaluation on the merits is even easier in our case, as all materials and methods for each project (including the full experiment) are easily accessible online. Second, the design of our course -- with multiple rounds of review by both more senior graduate students and a faculty member -- mirrors the typical structure of experimental work, where there are multiple sources of feedback from researchers at different career stages. In general, we don't see any reason why the career stage of the students in our class should be more of a concern in the current case than it is for other research.

In addition, our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear. For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials. In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample. And in some, differences of population would mean that followups would require further stimulus or task adaptation. More generally, we believe that our work here underscores the importance of iterated replication [@lewis2016].

@@

Our experiences performing and compiling the studies here sheds light on one further concern that we believe has been under-reported in past studies [including @osc2015]. Our standard model of replication is based on the notion of a single key statistical test -- and its associated effect size -- being the properties of a study that can be targeted for replication. Yet, as we mentioned above, selecting this "key test" was difficult for most of the projects in our sample, and virtually impossible for some. We were often forced to consult other sections of the papers (e.g., abstracts, discussion sections) to gain clarity on what test was considered the critical one for the authors' interpretation. It is likely that some of our decisions would not be ratified by the original authors.

@@

In our view, two recommendations will improve this situation dramatically. First, authors should specify their "key test" more clearly. Pre-registration might facilitate this step, as regstration typically requires the selection of particular statistical analyses to be designated as critical for interpretation, but we believe this designation is critical even in un-registered experiments. Had "key test" information been available, it would have dramatically simplified the problem of selecting the effect to replicate in several cases. Second, the widespread adoption of open data practices would dramatically facilitate the type of meta-research pursued here. In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is thus an important route for more flexible reuse.
